---
title: "index"
author: "Sida Chhun"
date: "5/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(plotly)
library(leaflet)
library(sp)
library(stringr)
library(data.table)
library(kableExtra)
library(knitr)
library(lintr)

# Reading shootings-2018 dataset into this file
shootings_2018 <- read.csv("data/shootings-2018.csv", stringsAsFactors = FALSE)

# Number of mass shootings occured in the 2018 shootings dataset
shootings_occured <- nrow(shootings_2018)

# Number of lives lost in 2018 due to mass shootings
lives_lost <- sum(shootings_2018$num_killed)

# City with the deadliest mass shooting in 2018
most_impacted_city <- shootings_2018 %>%
  filter(num_killed == 17) %>%
  select(city)
# Two other insights:

# 1. Rounded Average amount of injuries per mass shooting
avg_injuries_per_shooting <- round(mean(shootings_2018$num_injured))

# 2. Number of unique states affected within the country
number_of_states_affected <- length(unique(shootings_2018$state))

# Frequency of shooting filtered by state
state_frequency <- table(shootings_2018$state)

# Overall General shooting statistics in the US
general_shooting_stats <- data.frame(shootings_occured,
                                     lives_lost,
                                     avg_injuries_per_shooting,
                                     number_of_states_affected
)

# Condensed quickview of shooting in the US
Quick_View_Stats <- data.table(shootings_2018)

# Convert `state_frequency` to dataframe:
df_state_frequency <- data.frame(state_frequency)

# Number of Florida Mass Shootings
florida_shootings <- df_state_frequency[9, 2]

# Parkland Shooting Information:
parkland_information <- shootings_2018 [312, ]

# The date of the parkland shooting
parkland_date <- parkland_information$date

# The state of the parkland shooting
parkland_state <- parkland_information$state

# The city of the parkland shooting
parkland_city <- parkland_information$city

# The number killed in the parkland shooting
parkland_num_killed <- parkland_information$num_killed

# The number injured in the parkland shooting
parkland_num_injured <- parkland_information$num_injured

# Creating an Interactive Map

data <- read.csv("data/shootings-2018.csv")
data <- data[complete.cases(data), ]

data$long <- as.numeric(data$long)
data$lat <- as.numeric(data$lat)

data.sp <- SpatialPointsDataFrame(data[, c(7, 8)], data[, -c(7, 8)])

# Adding additional data to markers
map <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(data = data, lng = ~long, lat = ~lat,
             popup = paste("City:", data$city, "<br>",
                           "State:", data$state, "<br>",
                           "Number Killed:", data$num_killed, "<br>",
                           "Number Injured:", data$num_injured)
                           )

# Making a plot

mass_shootings_plot <- plot_ly(
  data = df_state_frequency, # data frame to show
  x = ~df_state_frequency$Freq, # variable for the x-axis,
  y = df_state_frequency$Var1, # variable for the y-axis
  type = "bar", # created a bar chart
  alpha = .7, # adjusted opacity
  hovertext = "y" # show the y-value when hovering over a bar
) %>%
  layout(
    title = "Bar-Chart of 2018 Mass Shootings Frequency by State",
    xaxis = list(title = "Total Mass Shootings"),
    yaxis = list(title = "States"))

```
#**Mass Shootings in the US**

Over the last decade, the frequency of mass shootings within the United States have soared significantly. This is a huge problem that is sadly becoming too commonplace within our country. The frequency of these mass shootings are desensitizing us to such tragic events forcing us to feel less and less shocked evertime a shooting occurs. **`r number_of_states_affected`** out of our 50 states have experienced these unfortunate attacks. Additionally, the average injury count per mass shooting is about **`r avg_injuries_per_shooting`**.
In 2018 alone, **`r shootings_occured`** mass shooting occured across the country, responsible for **`r lives_lost`** deaths on innocent citizens. The city impacted most by mass shootings (deadliest mass shooting) was **`r most_impacted_city`** with a total death toll of 17.

<font size="4"> **2018 Mass Shootings Overview:**</font> 
```{r general_shooting_stats, echo=FALSE}
general_shooting_stats %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("hover"))
```
 <font size="4"> **Table of all US Mass Shootings in 2018:**</font> 

```{r Quick_View_Stats, echo=FALSE}
kable(Quick_View_Stats[ , 1:6]) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

<font size="4"> **Particular Incident - Parkland, Florida High School Shooting**</font> 
A mass shooting that has made its way to the top three deadliest school shootings took place in **`r parkland_city`**, **`r parkland_state`** High School. Unfortunately, Florida as a state have encoutered these tregedies time and time again with a total amount of mass shootings equal to **`r florida_shootings`**. According to the [NY Daily News](https://www.nydailynews.com/news/national/deadliest-school-shootings-u-s-history-article-1.3821513), the Parkland shooting is the third most deadly school shooting in history not far behind the Sandy Hook Elementary shooting. Parkland's mass shooting caused a larger than usual outcry for improved gun laws and restrictions to be implemented. With that said, an article from the [NPR](https://www.npr.org/2019/02/14/694223232/poll-a-year-after-parkland-urgency-for-new-gun-restrictions-declines), presents a graph that tells a different story. The graph presented shows the urgency of implementing new gun restrictions with a poll over the last few decades. While the graph clearly shows a upward spike after the Parkland shooting, within a year; there has been a considerable downtrend, meaning the majority don't feel a strong urgency to change the current laws as much as they used to. 

 <font size="4"> **Map of US Mass Shootings in 2018:**</font> 

```{r map, echo=FALSE}
map
```
Upon click of any marker, you are given information about the particular mass shooting with significant information such as **City**, **State**, **Number of People Killed**, and **Number of People Injured**.

```{r mass_shootings_plot, echo=FALSE}
mass_shootings_plot
```
The reason for why I have chosen to use bar chart for my plot is because it allows me to show most of my states without the use of scrolling; which wouldn't be possibly with a histogram. Presenting the total mass shooting count on the x-axis helps the reader quickly understand the data presented as the y-axis already clearly presents states (both written out and titled). The bar-chart allows viewers to understand which states are at higher risks of mass shootings (e.g., California and Illinois) and which states aren't (e.g., Massachusetts and Delware).
