---
title: "Who Represents You?"
author: "Sida Chhun"
date: "5/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# civic-info.R
library(dplyr)
library(httr)
library(knitr)
library(kableExtra)
library(jsonlite)
library(lintr)

source("api-keys.R") # Load the script using a relative path

# Set the Base URI
civic_uri <- "https://www.googleapis.com/civicinfo/v2/"

# Set the Endpoint of my URI
endpoint1 <- paste0("representatives")

# Set my full URI including my API key
search_uri1 <- paste0(civic_uri, endpoint1, "?key=", google_api_key)

# Set the parameters for my URI
query_params <- list(
  address = "5000 25th Ave NE",
  k = google_api_key
)

# Use a GET function to gather information about my URI
response <- GET(
  search_uri1, query = query_params
)

# Check for Success (Code 200)
print(response)

# Extract content from response as a text string
response_text <- content(response, type = "text")

# Convert the JSON string to a list
response_data <- fromJSON(response_text)

# Checking to see if its already a data frame
is.data.frame(response_data) # FALSE

# Inspecting the data
str(response_data)

# Retrieving the names within the list
names(response_data)
# Returns the names "kind", "normalizedInput", "divisions", "offices",
# "officials"

# Finding names that are already data frames:
is.data.frame(response_data$kind) # False
is.data.frame(response_data$normalizedInput) # False
is.data.frame(response_data$divisions) # False
is.data.frame(response_data$offices) # TRUE - THIS IS VALUABLE!
is.data.frame(response_data$officials) # TRUE - THIS IS ALSO VALUABLE!

# Flattening the Offices data frame from response_data
offices <- flatten(response_data$offices)
# Flattening the Officials data frame from response_data
officials <- flatten(response_data$officials)

# Expanding "offices" dataframe by given indices 
num_to_rep <- unlist(lapply(response_data$offices$officialIndices, length))
expanded <- offices[rep (row.names (offices), num_to_rep), ]
new_officials <- officials %>% mutate(index = row_number()-1)
new_offices <- expanded %>% mutate(index = row_number() -1) %>% 
  rename(position = name)

# Selecting Only Necessary Columns from the "new_officials" Data Frame
new_officials <- select(new_officials, name, party, phones)

# Selecting Only Necessary Columns from the "Offices" Data Frame
select_offices <- select(new_offices, position)

# Renaming Single Column in "select_offices" Data Frame to "Position"
colnames(select_offices)[colnames(select_offices) == "name"] <- "Position"

# Renaming ALL columns names in "select_officials" Data Frame as Capitalized
colnames(new_officials) <- c("Name", "Party", "Phone")

# Adding Hyperlinks to Candidates' Names
Name <- paste0("[", (officials$name), "]",
                          "(", (officials$urls), ")")

# Convert "officials$emails" to Character rather than list
names(unlist(officials$emails))

# ifelse function to replace missing emails with the text "Not Available"
Email <- ifelse((officials$emails == "NULL"), paste0( "Not Available"),
                      paste0(officials$emails))


# ifelse function to replace missing photo urls with the text
# "No Picture Available"

Photo <- ifelse((is.na(officials$photoUrl) == F), paste0( 
  "![](", officials$photoUrl, ")"), paste0("No Photo Available"))

# Removing Names column from "new_officials" dataframe
final_officials <- new_officials[-1]


# Mutating All Data Frames Together
combined_data <- mutate(
  final_officials,
  Name,
  #select_offices,
  # KEEP GETTING ERROR: Column "select_offices" is of unsupported class
  # data.frame. No Google Search Results to match error.
  Email,
  Photo
)

# Rearranging Columns 
arranged_data <- arrange(combined_data, Party, Name,
                         Photo)


#-----------------------------------------------------------------------------
# propublica.R File

library(dplyr)
library(httr)
library(kableExtra)
library(jsonlite)
library(ggplot2)
library(lintr)

source("api-keys.R") # Load the Script using a relative path

# Assign my State a Variable
address <- "wa"

# Set the Base URI
propublica_uri <- "https://api.propublica.org/congress/v1"

# Set the endpoint of my URI
endpoint2 <- paste0("https://api.propublica.org/",
                    "congress/v1/members/house/wa/current.json")

# Set my full URI including my API Key
search_uri2 <- paste0(propublica_uri, endpoint2)

# Set the Parameters of my API
query_params2 <- (address2 <- "wa")

# Use a GET function to gather information about my URI
response2 <- GET(endpoint2, add_headers("X-API-Key" = propublica_api_key))

# Extract content from response as a text string
response_text2 <- content(response2, type = "text")

# Convert the JSON string to a list
response_data2 <- fromJSON(response_text2)

# Checking to see if its already a data frame
is.data.frame(response_data2) # FALSE

# Inspecting the data
str(response_data2)

# Retrieving the names within the list
names(response_data2)
# Returns the names "status", "copyright", "results"

# Finding names that are already data frames:
is.data.frame(response_data2$status) # False
is.data.frame(response_data2$copyright) # False
is.data.frame(response_data2$results) # TRUE - THIS IS VALUABLE!

# Flattening the "response_data$results" data frame
results <- flatten(response_data2$results)

# Assigning Male and Female representatives a Value
male_reps <- length(grep("M", results$gender)) # 5
female_reps <- length(grep("F", results$gender)) # 5

# Bar Plot that shows the number of Male and Female Representatives
# within the state. 
reps_by_gender_plot <- barplot( c(male_reps, female_reps),
        main = "Representatives by Gender
        within the State", names.arg = c("Male", "Female"))

# Assigning Democrat and Republican Representatives a Value
democrat <- length(grep("D", results$party)) # 7
republican <- length(grep("R", results$party)) # 3

# Bar Plot that shows the number of Democrats versus the number 
# of Republicans within the state. 
reps_by_party_plot <- barplot( c(democrat, republican),
        main = "Number of Democrat and Republican Representatives
        within the State", names.arg = c("Democrat", "Republican"))

#-------------------------------------------------------------------
  
# Set the Endpoint
endpoint3 <- paste0("https://api.propublica.org/congress/v1/",
                    "members/D000617.json")

# Use a GET function to gather information about my URI
response3 <- GET(endpoint3, add_headers("X-API-Key" = propublica_api_key))
  
# Extract content from response as a text string
response_text3 <- content(response3, type = "text")

# Convert the JSON string to a list
response_data3 <- fromJSON(response_text3)

# Checking to see if its already a dataframe
is.data.frame(response_data3) # False

names(response_data3)
is.data.frame(response_data3$status) # False
is.data.frame(response_data3$copyright) # False
is.data.frame(response_data3$results) # TRUE!

# Flattening the "response_data3$results" data frame
suzan <- flatten(response_data3$results)

#--------------------------------------------------------------------

# Set the Endpoint
endpoint4 <- paste0("https://api.propublica.org/congress/v1/members/D000617/",
                    "votes.json")

# Use a GET function to gather information about my URI
response4 <- GET(endpoint4, add_headers("X-API-Key" = propublica_api_key))

# Extract content from response as a text string
response_text4 <- content(response4, type = "text")

# Convert the JSON string to a list
response_data4 <- fromJSON(response_text4)

# Checking to see if its already a dataframe
is.data.frame(response_data4) # False

names(response_data4)
is.data.frame(response_data4$status) # False
is.data.frame(response_data4$copyright) # False
is.data.frame(response_data4$results) # TRUE!

# Flattening the "response_data4$results" data frame
suzan_votes <- flatten(response_data4$results)

# Making a Hyperlink for DelBene's Twitter Account
suzan_twitter <- paste0("[", "click here", "]", "(https://twitter.com/",
                                              "RepDelBene", ")" )

# How to calulate Suzan's Voting Percentage
suzan_total_votes <- suzan_votes$votes[[1]][["position"]]

suzan_yes <- length(grep("Yes", suzan_total_votes)) # 16
suzan_no <- length(grep("No", suzan_total_votes)) # 4
```
## Your Representatives
This report contains data from the [ProPublica API](https://projects.propublica.org/api-docs/congress-api/) along with the [Google Civic Data API](https://developers.google.com/civic-information/). The address that I have assigned to this report is one of the UW Apartments; **Nordheim Court**. This report will display the representatives; depending on the **Given Address**



```{r kable(arranged_data), echo=FALSE}
kable(arranged_data) %>% 
kable_styling(bootstrap_options = c("striped", "hover"))
```




```{r select_offices, echo=FALSE}
kable(select_offices)
```


## House of Representatives
Moving on to the House of Representatives we have plotted a couple of bar charts
for your viewing. The first chart shows the gender diverity of the
Representatives within the State. The next chart displays the number of 
**Democrat** and **Republican** Representatives in the State. 

```{r reps_by_gender_plot, echo=FALSE}
reps_by_gender_plot <- barplot( c(male_reps, female_reps),
        main = "Representatives by Gender
        within the State", names.arg = c("Male", "Female"))
```

```{r reps_by_party_plot, echo=FALSE}
reps_by_party_plot <- barplot( c(democrat, republican),
        main = "Number of Democrat and Republican Representatives
        within the State", names.arg = c("Democrat", "Republican"))
```

## Suzan DelBene
According to the ProPublica API, Suzan DelBene is a U.S. Congresswoman focusing 
on a variety of significant issues including Jobs and the Economy, Veterans, 
Agriculture, the Environment, and more. DelBene has a date of birth equal to
**`r suzan$date_of_birth`** which would make her **57 years old** today. To keep
up with DelBene, just `r suzan_twitter` to be automatically directed to
DelBene's Twitter Account. Within the last 20 votes DelBene has participated in,
she's approved 16 of them giving her an vote yes percentage of **80%**.

